### 2025-08-12 download-football-data.qmd
20250812 - unlink figures

::: {#fig-projectionsTabFFA}
[![](images/projectionsTab.png){fig-alt="Fantasy Football Projections Available From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>."}](https://apps.fantasyfootballanalytics.net)

>>>>

::: {#fig-projectionsTabFFA}
![](images/projectionsTab.png){fig-alt="Fantasy Football Projections Available From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>."}

### 2025-08-12 draft.qmd
20250812 - unlink figures

::: {#fig-snakeDraftToolFFA}
![](images/snakeDraftTool.png){fig-alt="Free Snake Draft Tool From Fantasy Football Analytics. From <https://apps.fantasyfootballanalytics.net>."}

Free Snake Draft Tool From Fantasy Football Analytics. From <https://apps.fantasyfootballanalytics.net>.
:::

>>>>

::: {#fig-snakeDraftToolFFA}
![](images/snakeDraftTool.png){fig-alt="Free Snake Draft Tool From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>."}

Free Snake Draft Tool From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>.
:::
